\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-11-10 article.tex
kinship2 second response

We demonstrate how the standardized pedigree charts in the \pkg{kinship2} package generate ambiguous results in such scenarios by superimposing a hypothetical inter-generational breeding case in Figure \ref{fig:kinshipFig}. In that figure, each generation is defined by its position on the vertical axis, with the first generation containing individuals 201 and 202. We superimposed green-highlighted individual 215 onto the pedigree chart for explanatory purposes. Its parents are individuals 201 and 206, which are from generations one and two, respectively, and have a parent-child relationship between themselves. As an offspring of a parent-child relationship, individual 215 is both a second and third generation individual. Hence, individual 215 should be displayed in both second and third generational positions on the vertical axis. However, standard pedigree tools only allow for an individual to be displayed once. As a result, in special cases where inter-generational breading occurs, such as in agronomic applications, most standardized tools for visualizing genealogical information ambiguously portray the genealogical dataset.

In the \pkg{kinship2} package, if an individual cannot be represented with only one instance, then it will be completely copied and connected with dotted lines to relevant individuals. However, the package requires that each child has exactly zero or two parents; if a child has two parents, then one must be female and one must be male. These requirements preclude certain genealogical datasets from being plotted by generation count, especially when their complexity increases with inter-generational breeding.

\begin{figure}[H]
    \centering
    \fbox{\includegraphics[width=0.65\textwidth]{kinshipFig}}
    \caption{Example pedigree chart from the \pkg{kinship2} package, where the vertical axis denotes generation count. We superimposed green-highlighted individual 215 for explanatory purposes. As an offspring of a parent-child relationship, individual 215 is both a second and third generation individual. Hence, it should be displayed twice on the vertical axis, once for each of its generation counts. However, most standard pedigree tools only allow for an individual to be displayed once. In the \pkg{kinship2} package, individuals can be displayed more than once. However, each child must have zero or two parents (one male and one female). These restrictions make it impossible to plot genealogical data by generation count in cases where there are many inter-generational breedings.
    \label{fig:kinshipFig}
\end{figure}

>>>>

We demonstrate how the standardized pedigree charts in the \pkg{kinship2} package generate ambiguous results in such scenarios by superimposing a hypothetical inter-generational breeding case in Figure \ref{fig:kinshipFig}. In that figure, each generation is defined by its position on the vertical axis, with the first generation containing individuals 201 and 202. We superimposed green-highlighted individual 215 onto the pedigree chart for explanatory purposes. Its parents are individuals 201 and 206, which are from generations one and two, respectively, and have a parent-child relationship between themselves. As an offspring of a parent-child relationship, individual 215 is both a second and third generation individual. Hence, individual 215 should be displayed in both second and third generational positions on the vertical axis. However, most standard pedigree tools only allow for an individual to be displayed once. As a result, in special cases where inter-generational breading occurs, such as in agronomic applications, most standardized tools for visualizing genealogical information ambiguously portray the genealogical dataset by generation count.

In the \pkg{kinship2} package, if an individual cannot be represented with only one instance, then it will be completely copied and connected with dotted lines to the relevant individuals. However, the package requires that each child has exactly zero or two parents; if a child has two parents, then one must be female and one must be male. These requirements preclude certain genealogical datasets from being plotted by generation count, especially when their complexity increases with inter-generational breeding.

\begin{figure}[H]
    \centering
    \fbox{\includegraphics[width=0.65\textwidth]{kinshipFig}}
    \caption{Example pedigree chart from the \pkg{kinship2} package, where the vertical axis denotes generation count. We superimposed green-highlighted individual 215 for explanatory purposes. As an offspring of a parent-child relationship, individual 215 is both a second and third generation individual. Hence, it should be displayed twice on the vertical axis, once for each of its generation counts. However, most standard pedigree tools only allow for an individual to be displayed once. In the \pkg{kinship2} package, individuals can indeed be displayed more than once. However, each child must have zero or two parents (one male and one female). These restrictions make it impossible to plot genealogical data by generation count in cases where there are many inter-generational breedings.
    \label{fig:kinshipFig}
\end{figure}
